\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{same}
\setlength{\tabcolsep}{0in}
\raggedbottom
\raggedright

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Resume Starts Here
\begin{document}

\begin{center}
  {\Huge \scshape Max Heitzman} \\ \vspace{1pt}
  \small Lubbock, TX $|$ \href{mailto:maxheitzman@ttu.edu}{maxheitzman@ttu.edu} $|$ \href{https://github.com/maxheitzman}{github.com/maxheitzman} $|$ \href{https://linkedin.com/in/maxheitzman}{linkedin.com/in/maxheitzman}
\end{center}

% EDUCATION
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Texas Tech University}{Lubbock, TX}
    {B.S. Computer Science, Minor in Mathematics}{Expected: Dec 2025}
\resumeSubHeadingListEnd

% EXPERIENCE
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Sales Associate – Concert Merchandising}{Jun 2020 -- Present}
    {River City Merchandising}{Nationwide}
    \resumeItemListStart
      \resumeItem{Supported high-volume sales operations at live events across multiple venues.}
      \resumeItem{Handled cash, POS systems, inventory management, and upselling under pressure.}
      \resumeItem{Developed excellent customer service and interpersonal skills in fast-paced environments.}
    \resumeItemListEnd

  \resumeSubheading
    {IT Assistant}{Jun 2018 -- Oct 2019}
    {Texas Neurology, PA}{Dallas, TX}
    \resumeItemListStart
      \resumeItem{Assisted with digitization of sensitive medical records and data entry.}
      \resumeItem{Supported small-scale tech tasks and IT system organization.}
    \resumeItemListEnd

  \resumeSubheading
    {Food Service Provider}{Summer 2017}
    {Lakewood Country Club}{Dallas, TX}
    \resumeItemListStart
      \resumeItem{Performed front-line service and closing procedures in a high-traffic environment.}
      \resumeItem{Learned to manage fast customer flow while maintaining service quality.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

% PROJECTS
\section{Projects}
\resumeSubHeadingListStart
  \resumeSubheading
    {Multiprocessor Cellular Automaton Simulator}{Apr 2025}
    {Python | Parallel Programming}{GitHub}
    \resumeItemListStart
      \resumeItem{Built a two-phase simulator that evolves matrix state based on symbolic rules.}
      \resumeItem{Phase 1: Single-threaded prototype used to validate rules and logic.}
      \resumeItem{Phase 2: Implemented parallel processing with Python’s multiprocessing module.}
    \resumeItemListEnd

  \resumeSubheading
    {Syntax Parser}{Mar 2025}
    {C | Compiler Design}{GitHub}
    \resumeItemListStart
      \resumeItem{Built a recursive descent parser that validates grammar rules using BNF.}
      \resumeItem{Reads from a custom token stream generated by a lexical analyzer.}
    \resumeItemListEnd

  \resumeSubheading
    {Lexical Analyzer}{Feb 2025}
    {C | Language Processing}{GitHub}
    \resumeItemListStart
      \resumeItem{Scans and classifies lexemes as keywords, identifiers, literals, or operators.}
      \resumeItem{Handles syntax edge cases and symbolic character streams.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

% SKILLS
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{
    \item{
      \textbf{Languages}{: C, Python, Java} \\
      \textbf{Tools}{: Git, VS Code, Overleaf, MobaXterm, Eclipse, Code::Blocks, PyCharm} \\
      \textbf{Concepts}{: Lexical Analysis, Parsing, Recursion, Multiprocessing, Customer Experience}
    }
  }
\end{itemize}

% ORGANIZATIONS
\section{Organizations}
\resumeSubHeadingListStart
  \resumeSubheading
    {Google Developer Student Club (GDSC)}{Aug 2023 – Present}
    {Member, Texas Tech University}{}
  \resumeSubheading
    {Association for Computing Machinery (ACM)}{Aug 2023 – Present}
    {Member, Texas Tech University}{}
\resumeSubHeadingListEnd

% VOLUNTEER EXPERIENCE
\section{Volunteer Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Volunteer Sales \& Support Assistant}{Summer 2022}
    {Disabled American Veterans Thrift Store}{Dallas, TX}
    \resumeItemListStart
      \resumeItem{Contributed 120+ hours assisting customers, organizing inventory, and supporting retail displays.}
      \resumeItem{Strengthened communication and interpersonal skills while serving diverse community members.}
    \resumeItemListEnd

  \resumeSubheading
    {Student Support Volunteer}{Aug 2018 – May 2019}
    {Apollo Junior High School}{Richardson, TX}
    \resumeItemListStart
      \resumeItem{Provided in-class support for students with disabilities to foster inclusive learning.}
      \resumeItem{Developed patience and adaptability while assisting with learning tasks and peer engagement.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
